Rstudio in Data Science and Paper Writing

### 2024-11-11 manuscript/Manuscript.qmd
MS, presentation: edits, update git slide

---
title: "Paper or report template"
subtitle: |
  \raggedright  Author 1^1,2,\*^ , Author 2^1,2^, Author 3^3^, Author 4E^4^ \newline<br>^1^Heidelberg University, Centre for Organismal Studies (COS), 69120 Heidelberg, Germany \newline<br>^2^Affiliation 2 \newline<br>^3^Affiliation 3 \newline<br>^4^Affiliation 4\newline<br>  ^\*^Correspondence: xy@cos.uni-heidelberg.de
mainfont: Arial
monofont: DejaVu Sans Mono #Times New Roman
fontsize: 11pt
linestretch: 1.2
linkcolor: blue
documentclass: article
crossref:
  fig-title: Figure     # (default is "Figure")
max-width: 100%
format:
  html: 
    embed-resources: true
  pdf:
    pdf-engine: xelatex
    number-sections: false
    margin-left: 0.8in
    margin-right: 0.8in
    margin-top: 0.8in
    margin-bottom: 0.8in
    toc: true
    keep-tex: true
    include-in-header:
      text: |
        \usepackage{lineno}
    include-before-body:
      text: |
        \linenumbers
bibliography: references.bib #add bibliography in this file
csl: elife.csl #change according to journal
---

@@

Here is our abstract. We discovered that medaka fish can eat Arabidpopsis shoop apical meristeme cells to regulate energy metabolism (data not shown).
Here is some **text in bold** *italic* [underline]{.underline} and ^superscript^.

# Introduction

@@

@@

@@

@@

Now edit the text, add a few references and press -> Render and see how the changes show up on the rendered document.
It is easier and faster to render your document to html. You will get a very nice dynamic layout that you can read in the browser (use Firefox). You can also render into pdf, but you need to install a version of latex for that. An easy alternative to generate a nice pdf is to open the html version in a browser (in this case Chrome gives the best results) and print to a pdf file.

@@

knitr::include_graphics("figures/Figure_complex.png")
```

@@

Inserting comments: <!--# I don't agree here -->
You can also use the visual editor and insert -> comment.

@@

We would like to thank the [Jekely lab](https://github.com/JekelyLab) for the [R project template](<https://github.com/JekelyLab/new_paper_template>) we used to write this paper. This work was funded by xy funding agency.

@@

@@

```{=html}
<!--
## See https://github.com/hypothesis/client
## Add commenting functionality with this script
-->
```
```{=html}
<script src="hypothes.is/embed.js" async></script>
```

>>>>

---
title: "Paper or report template"
subtitle: |
  \raggedright  Author 1^1,2,\*^ , Author 2^1,2^, Author 3^3^, Author 4E^4^ \newline<br>^1^Heidelberg University, Centre for Organismal Studies (COS), 69120 Heidelberg, Germany \newline<br>^2^Affiliation 2 \newline<br>^3^Affiliation 3 \newline<br>^4^Affiliation 4\newline<br>  ^\*^Correspondence: xy@cos.uni-heidelberg.de
mainfont: Arial
monofont: DejaVu Sans Mono #Times New Roman
fontsize: 11pt
linestretch: 1.2
linkcolor: blue
documentclass: article
crossref:
  fig-title: Figure     # (default is "Figure")
format:
  html: 
    embed-resources: true
  pdf:
    pdf-engine: xelatex
    number-sections: false
    margin-left: 0.8in
    margin-right: 0.8in
    margin-top: 0.8in
    margin-bottom: 0.8in
    toc: true
    keep-tex: true
    include-in-header:
      text: |
        \usepackage{lineno}
    include-before-body:
      text: |
        \linenumbers
bibliography: references.bib #add bibliography in this file
csl: development.csl #change according to journal
---

@@

Here is our **abstract**. We *discovered* that `medaka` fish can eat Arabidpopsis shoop apical meristeme cells to regulate energy metabolism (data not shown). Here is some **text in bold** *italic* [underline]{.underline} and ^superscript^.

## Introduction

## Sub-intro

### Sub-sub-intr

###### sub-sub-sub-intro

##### sub-sub-sub-sub-intro

@@

it is just like ms word, let's add a reference [@lyndby2023; @Pavlov2006] another one [@Marino2004; @Pavlov2006] [@Saile2023; @ozpolat2021]

@@

Histology of the crocodile [@myburgh2023]

@@

Nile croc paper [@pooley1976nile]

@@

Now edit the text, add a few references and press -\> Render and see how the changes show up on the rendered document. It is easier and faster to render your document to html. You will get a very nice dynamic layout that you can read in the browser (use Firefox). You can also render into pdf, but you need to install a version of latex for that. An easy alternative to generate a nice pdf is to open the html version in a browser (in this case Chrome gives the best results) and print to a pdf file.

@@

knitr::include_graphics("figures/Figure_scalebars_gap.png")
```

@@

Inserting comments: <!--# I don't agree here --> You can also use the visual editor and insert -\> comment.

@@

We would like to thank the [Jekely lab](https://github.com/JekelyLab) for the [R project template](https://github.com/JekelyLab/new_paper_template) we used to write this paper. This work was funded by xy funding agency.

@@

## A table from tablesgenerator

| gene   | days | raw_data | ct_value | dt_ct              | x2_dct               | mean2dct             | sd2dct               |
|--------|------|----------|----------|--------------------|----------------------|----------------------|----------------------|
| Nanog  | d0   | J1       | 22,491   | 6,956000000000000  | 0,008054439990584290 | 0,080889155034072582 | 9,40847959654144e-02 |
| Nanog  | d0   | J2       | 19,877   | 4,395999999999999  | 0,047497651762547402 | 0,080889155034072582 | 9,40847959654144e-02 |
| Nanog  | d0   | J3       | 19,164   | 2,418000000000003  | 0,187115373349086067 | 0,080889155034072582 | 9,40847959654144e-02 |
| Nanog  | d7   | J4       | 21,177   | 4,667999999999999  | 0,039336161672026825 | 0,031927117712361432 | 7,83151167074938e-03 |
| Nanog  | d7   | J5       | 21,812   | 4,934000000000001  | 0,032712821311705470 | 0,031927117712361432 | 7,83151167074938e-03 |
| Nanog  | d7   | J6       | 22,303   | 5,397000000000002  | 0,023732370153351993 | 0,031927117712361432 | 7,83151167074938e-03 |
| Nanog  | d11  | J7       | 22,930   | 7,436000000000000  | 0,005774853247163445 | 0,145298820021575043 | 2,41582234272199e-01 |
| Nanog  | d11  | J8       | 22,915   | 7,412999999999998  | 0,005867655964613011 | 0,145298820021575043 | 2,41582234272199e-01 |
| Nanog  | d11  | J9       | 17,831   | 1,236999999999998  | 0,424253950852948647 | 0,145298820021575043 | 2,41582234272199e-01 |
| Nanog  | d15  | J10      | 15,848   | 1,252000000000001  | 0,419865746472069978 | 0,159625405875477383 | 2,25708832493508e-01 |
| Nanog  | d15  | J11      | 20,295   | 4,581000000000001  | 0,041781265481410403 | 0,159625405875477383 | 2,25708832493508e-01 |
| Nanog  | d15  | J12      | 20,492   | 5,859000000000002  | 0,017229205672951744 | 0,159625405875477383 | 2,25708832493508e-01 |
| Nanog  | d16  | J13      | 21,168   | 5,347999999999999  | 0,024552266145861899 | 0,036597442578737135 | 1,04525811603947e-02 |
| Nanog  | d16  | J14      | 20,984   | 4,575000000000003  | 0,041955390711883152 | 0,036597442578737135 | 1,04525811603947e-02 |
| Nanog  | d16  | J15      | 20,974   | 4,530000000000001  | 0,043284670878466366 | 0,036597442578737135 | 1,04525811603947e-02 |
| oct4   | d0   | K1       | 17,910   | 2,375000000000000  | 0,192776353175992593 | 0,311031348034201960 | 1,83714182145261e-01 |
| oct4   | d0   | K2       | 17,681   | 2,200000000000001  | 0,217637640824030865 | 0,311031348034201960 | 1,83714182145261e-01 |
| oct4   | d0   | K3       | 17,682   | 0,936000000000000  | 0,522680050102582450 | 0,311031348034201960 | 1,83714182145261e-01 |
| oct4   | d7   | K4       | 21,113   | 4,603999999999999  | 0,041120453907156532 | 0,049755310269836310 | 1,48819426940308e-02 |
| oct4   | d7   | K5       | 21,479   | 4,600999999999999  | 0,041206050452886472 | 0,049755310269836310 | 1,48819426940308e-02 |
| oct4   | d7   | K6       | 20,807   | 3,901000000000000  | 0,066939426449465933 | 0,049755310269836310 | 1,48819426940308e-02 |
| oct4   | d11  | K7       | 19,617   | 4,123000000000001  | 0,057392260143807688 | 0,090862010483616931 | 4,52910618365094e-02 |
| oct4   | d11  | K8       | 19,282   | 3,779999999999999  | 0,072795849154278516 | 0,090862010483616931 | 4,52910618365094e-02 |
| oct4   | d11  | K9       | 19,406   | 2,811999999999998  | 0,142397922152764589 | 0,090862010483616931 | 4,52910618365094e-02 |
| oct4   | d15  | K10      | 18,640   | 4,044000000000000  | 0,060622619396358407 | 0,089412757950352861 | 4,08917973218200e-02 |
| oct4   | d15  | K11      | 18,590   | 2,875999999999999  | 0,136219014026666085 | 0,089412757950352861 | 4,08917973218200e-02 |
| oct4   | d15  | K12      | 18,441   | 3,808000000000000  | 0,071396640428034092 | 0,089412757950352861 | 4,08917973218200e-02 |
| oct4   | d16  | K13      | 19,843   | 4,023000000000000  | 0,061511501377112525 | 0,121511212049720957 | 5,39049236892096e-02 |
| oct4   | d16  | K14      | 19,001   | 2,592000000000002  | 0,165855642574644940 | 0,121511212049720957 | 5,39049236892096e-02 |
| oct4   | d16  | K15      | 19,310   | 2,866000000000000  | 0,137166492197405399 | 0,121511212049720957 | 5,39049236892096e-02 |
| sox2   | d0   | L1       | 22,212   | 6,677000000000000  | 0,009772883438384896 | 0,012106883312601676 | 5,00188213381361e-03 |
| sox2   | d0   | L2       | 22,326   | 6,845000000000001  | 0,008698606392411608 | 0,012106883312601676 | 5,00188213381361e-03 |
| sox2   | d0   | L3       | 22,554   | 5,808000000000000  | 0,017849160107008523 | 0,012106883312601676 | 5,00188213381361e-03 |
| sox2   | d7   | L4       | 23,729   | 7,219999999999999  | 0,006707542472169956 | 0,008115146531345131 | 1,23319175000228e-03 |
| sox2   | d7   | L5       | 23,673   | 6,794999999999998  | 0,009005362084366138 | 0,008115146531345131 | 1,23319175000228e-03 |
| sox2   | d7   | L6       | 23,762   | 6,856000000000002  | 0,008632535037499301 | 0,008115146531345131 | 1,23319175000228e-03 |
| sox2   | d11  | L7       | 23,290   | 7,795999999999999  | 0,004499561102927181 | 0,005068258267873239 | 1,39821485937085e-03 |
| sox2   | d11  | L8       | 23,452   | 7,950000000000001  | 0,004044003608755378 | 0,005068258267873239 | 1,39821485937085e-03 |
| sox2   | d11  | L9       | 23,824   | 7,230000000000000  | 0,006661210091937160 | 0,005068258267873239 | 1,39821485937085e-03 |
| sox2   | d15  | L10      | 18,978   | 4,382000000000001  | 0,047960815500027662 | 0,019052009679567623 | 2,50790414471593e-02 |
| sox2   | d15  | L11      | 23,078   | 7,363999999999999  | 0,006070369287375391 | 0,019052009679567623 | 2,50790414471593e-02 |
| sox2   | d15  | L12      | 22,955   | 8,321999999999999  | 0,003124844251299816 | 0,019052009679567623 | 2,50790414471593e-02 |
| sox2   | d16  | L13      | 18,256   | 2,436000000000000  | 0,184795303909230241 | 0,065112130982845073 | 1,03648699316095e-01 |
| sox2   | d16  | L14      | 23,955   | 7,545999999999999  | 0,005350910077990494 | 0,065112130982845073 | 1,03648699316095e-01 |
| sox2   | d16  | L15      | 24,034   | 7,590000000000000  | 0,005190178961314499 | 0,065112130982845073 | 1,03648699316095e-01 |
| Nestin | d0   | M1       | 25,678   | 10,143000000000001 | 0,000884408186540842 | 0,001005919450970835 | 3,78037724925826e-04 |
| Nestin | d0   | M2       | 25,954   | 10,473000000000001 | 0,000703578978924766 | 0,001005919450970835 | 3,78037724925826e-04 |
| Nestin | d0   | M3       | 26,196   | 9,450000000000003  | 0,001429771187446897 | 0,001005919450970835 | 3,78037724925826e-04 |
| Nestin | d7   | M4       | 26,637   | 10,128000000000000 | 0,000893651531374930 | 0,001047338646785763 | 1,49154536320385e-04 |
| Nestin | d7   | M5       | 26,591   | 9,713000000000001  | 0,001191504404562717 | 0,001047338646785763 | 1,49154536320385e-04 |
| Nestin | d7   | M6       | 26,792   | 9,886000000000003  | 0,001056860004419641 | 0,001047338646785763 | 1,49154536320385e-04 |
| Nestin | d11  | M7       | 25,344   | 9,850000000000001  | 0,001083563937566254 | NA                   | NA                   |
| Nestin | d11  | M8       | 25,548   | 10,045999999999998 | 0,000945916200416630 | NA                   | NA                   |
| Nestin | d11  | M9       | NA       | NA                 | NA                   | NA                   | NA                   |
| Nestin | d15  | M10      | 25,146   | 10,550000000000001 | 0,000667011844118357 | 0,040212093347121759 | 6,78034116386107e-02 |
| Nestin | d15  | M11      | 25,128   | 9,414000000000000  | 0,001465897556166378 | 0,040212093347121759 | 6,78034116386107e-02 |
| Nestin | d15  | M12      | 17,710   | 3,077000000000002  | 0,118503370641080533 | 0,040212093347121759 | 6,78034116386107e-02 |
| Nestin | d16  | M13      | 26,670   | 10,850000000000001 | 0,000541781968783127 | 0,000811307199498398 | 2,34037441161003e-04 |
| Nestin | d16  | M14      | 26,481   | 10,072000000000003 | 0,000929021754230271 | 0,000811307199498398 | 2,34037441161003e-04 |
| Nestin | d16  | M15      | 26,464   | 10,020000000000000 | 0,000963117875481796 | 0,000811307199498398 | 2,34037441161003e-04 |
| pax6   | d0   | N1       | 28,141   | 12,605999999999998 | 0,000160404251361007 | 0,000202563640616283 | 9,07049173589390e-05 |
| pax6   | d0   | N2       | 28,277   | 12,796000000000001 | 0,000140611284466474 | 0,000202563640616283 | 9,07049173589390e-05 |
| pax6   | d0   | N3       | 28,417   | 11,671000000000003 | 0,000306675386021368 | 0,000202563640616283 | 9,07049173589390e-05 |
| pax6   | d7   | N4       | 26,551   | 10,041999999999998 | 0,000948542476114878 | 0,001113850118374157 | 2,12530157522733e-04 |
| pax6   | d7   | N5       | 26,407   | 9,529000000000000  | 0,001353583872705483 | 0,001113850118374157 | 2,12530157522733e-04 |
| pax6   | d7   | N6       | 26,816   | 9,910000000000000  | 0,001039424006302109 | 0,001113850118374157 | 2,12530157522733e-04 |
| pax6   | d11  | N7       | 26,240   | 10,745999999999999 | 0,000582279722817692 | 0,000832785029034435 | 3,78505530767820e-04 |
| pax6   | d11  | N8       | 26,094   | 10,592000000000001 | 0,000647873603807208 | 0,000832785029034435 | 3,78505530767820e-04 |
| pax6   | d11  | N9       | 26,217   | 9,622999999999998  | 0,001268201760478404 | 0,000832785029034435 | 3,78505530767820e-04 |
| pax6   | d15  | N10      | 24,989   | 10,393000000000001 | 0,000743695673683233 | 0,000925553902054457 | 4,08653936584204e-04 |
| pax6   | d15  | N11      | 25,201   | 9,487000000000000  | 0,001393568853240116 | 0,000925553902054457 | 4,08653936584204e-04 |
| pax6   | d15  | N12      | 25,244   | 10,611000000000001 | 0,000639397179240022 | 0,000925553902054457 | 4,08653936584204e-04 |
| pax6   | d16  | N13      | 25,234   | 9,414000000000001  | 0,001465897556166376 | 0,118332806864036216 | 2,01592584300493e-01 |
| pax6   | d16  | N14      | 25,099   | 8,690000000000001  | 0,002421304101443331 | 0,118332806864036216 | 2,01592584300493e-01 |
| pax6   | d16  | N15      | 17,954   | 1,510000000000002  | 0,351111218934498925 | 0,118332806864036216 | 2,01592584300493e-01 |
| Foxg1  | d0   | O1       | 27,995   | 12,460000000000001 | 0,000177486879555702 | 0,000282945149618699 | 1,74962623637300e-04 |
| Foxg1  | d0   | O2       | 27,870   | 12,389000000000001 | 0,000186440124262781 | 0,000282945149618699 | 1,74962623637300e-04 |
| Foxg1  | d0   | O3       | 27,756   | 11,010000000000002 | 0,000484908445037615 | 0,000282945149618699 | 1,74962623637300e-04 |
| Foxg1  | d7   | O4       | 27,679   | 11,169999999999998 | 0,000434005215413365 | 0,000523746522152919 | 8,78322810890892e-05 |
| Foxg1  | d7   | O5       | 27,766   | 10,887999999999998 | 0,000527697950214528 | 0,000523746522152919 | 8,78322810890892e-05 |
| Foxg1  | d7   | O6       | 27,586   | 10,680000000000000 | 0,000609536400830865 | 0,000523746522152919 | 8,78322810890892e-05 |
| Foxg1  | d11  | O7       | 27,338   | 11,844000000000001 | 0,000272019934282063 | 0,288184521683127526 | 4,98617302108864e-01 |
| Foxg1  | d11  | O8       | 27,010   | 11,508000000000001 | 0,000343357714822539 | 0,288184521683127526 | 4,98617302108864e-01 |
| Foxg1  | d11  | O9       | 16,805   | 0,210999999999999  | 0,863938187400278057 | 0,288184521683127526 | 4,98617302108864e-01 |
| Foxg1  | d15  | O10      | 26,363   | 11,766999999999999 | 0,000286932697368108 | 0,000345700735619899 | 1,54341824432769e-04 |
| Foxg1  | d15  | O11      | 26,621   | 10,906999999999998 | 0,000520793838296761 | 0,000345700735619899 | 1,54341824432769e-04 |
| Foxg1  | d15  | O12      | 26,723   | 12,090000000000000 | 0,000229375671194827 | 0,000345700735619899 | 1,54341824432769e-04 |
| Foxg1  | d16  | O13      | 26,943   | 11,123000000000001 | 0,000448377032373498 | 0,000619126191915002 | 1,48774900949806e-04 |
| Foxg1  | d16  | O14      | 26,847   | 10,438000000000002 | 0,000720856643399820 | 0,000619126191915002 | 1,48774900949806e-04 |
| Foxg1  | d16  | O15      | 26,949   | 10,505000000000003 | 0,000688144899971688 | 0,000619126191915002 | 1,48774900949806e-04 |
| GAPDH  | d0   | P1       | 15,535   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
| GAPDH  | d0   | P2       | 15,481   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
| GAPDH  | d0   | P3       | 16,746   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
| GAPDH  | d7   | P4       | 16,509   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
| GAPDH  | d7   | P5       | 16,878   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
| GAPDH  | d7   | P6       | 16,906   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
| GAPDH  | d11  | P7       | 15,494   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
| GAPDH  | d11  | P8       | 15,502   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
| GAPDH  | d11  | P9       | 16,594   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
| GAPDH  | d15  | P10      | 14,596   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
| GAPDH  | d15  | P11      | 15,714   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
| GAPDH  | d15  | P12      | 14,633   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
| GAPDH  | d16  | P13      | 15,820   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
| GAPDH  | d16  | P14      | 16,409   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |
| GAPDH  | d16  | P15      | 16,444   | 0,000000000000000  | 1,000000000000000000 | 1,000000000000000000 | 0,00000000000000e+00 |

@@

<!--
## See https://github.com/hypothesis/client
## Add commenting functionality with this script
-->
<script src="hypothes.is/embed.js" async></script>

### 2024-11-11 manuscript/Manuscript.tex
MS, presentation: edits, update git slide

The references are stored in manuscript/references.bib (need to be
defined in the Yaml header). This file will automatically updated when
you insert a new reference through the Visual editor \textgreater{}
Insert \textgreater{} Citations.

@@

You can add your figures into the rendered document. We saved the
figures into /manuscript/figures or /manuscript/figure\_supplements and
can insert them from there. We use knitr::include\_graphics for this.
The title and legend can also be edited, as will as the width of the
output figure. Test comment behaviour:

>>>>

The references are stored in manuscript/references.bib (needs to be
defined in the Yaml header). This file will automatically updated when
you insert a new reference through the Visual editor \textgreater{}
Insert \textgreater{} Citations.

@@

You can add your figures into the rendered document. We saved the
figures into /manuscript/figures or /manuscript/figure\_supplements and
can insert them from there. We use knitr::include\_graphics for this.
The title and legend can also be edited, as well as the width of the
output figure.

### 2024-11-11 manuscript/Test_quarto.qmd
MS, presentation: edits, update git slide

---
title: "table_test"
format: html
---

## Quarto

@@

## Table

|   |   |   |   |   |
|---|---|---|---|---|
|   |   |   |   |   |
|   |   |   |   |   |
|   |   |   |   |   |

| Reagent type (species) or resource         | Designation                                        | Source or reference                                                                                | Identifiers          | Additional information                                                                                           |
|--------------------------------------------|----------------------------------------------------|----------------------------------------------------------------------------------------------------|----------------------|------------------------------------------------------------------------------------------------------------------|
|                                            |                                                    |                                                                                                    |                      |                                                                                                                  |
| biological sample (N. vectensis)           | larval, juvenile and adult N. vectensis            | Specimens obtained form the Marine Invertebrate Culture Unit of the University of Exeter           | N/A                  |                                                                                                                  |
| biological sample (cDNA)                   | cDNA obtained from N. vectensis                    | this study                                                                                         | N/A                  | RNA extracted with Trizol and cDNA synthesized with cDNA synthesis kit according to manufacturers recommendation |
| biological sample (peptide extract)        | peptide extracts obtained from N. vectensis        | this study                                                                                         | N/A                  | Peptides extracted from N. vectensis according to protocol explained in Material and Methods                     |
| genetic reagent (cDNA synthesis)           | SuperScript™ III First-Strand Synthesis System     | Invitrogen (from ThermoFisher)                                                                     | 18080051             |                                                                                                                  |
| genetic reagent (Polymerase)               | Q5® Hot Start High-Fidelity DNA Polymerase         | New England Biolabs                                                                                | M0493L               |                                                                                                                  |
| genetic reagent (DNA assembly)             | NEBuilder® HiFi DNA Assembly Master Mix            | New England Biolabs                                                                                | E2621L               |                                                                                                                  |
| genetic reagent (restriction enzyme)       | EcoRV restriction enzyme                           | New England Biolabs                                                                                | R3195L               |                                                                                                                  |
| genetic reagent (restriction enzyme)       | Afl2 restriction enzyme                            | New England Biolabs                                                                                | R0520L               |                                                                                                                  |
| genetic reagent (restriction enzyme)       | Hind3 restriction enzyme                           | New England Biolabs                                                                                | R3104L               |                                                                                                                  |
| genetic reagent (restriction enzyme)       | BamH1 restriction enzyme                           | New England Biolabs                                                                                | R3136L               |                                                                                                                  |
| genetic reagent (restriction enzyme)       | EcoRI restriction enzyme                           | New England Biolabs                                                                                | R3101L               |                                                                                                                  |
| recombinant DNA reagent (plasmid)          | pcDNA3.1(+)                                        | Invitrogen (from ThermoFisher)                                                                     | V79020               |                                                                                                                  |
| recombinant DNA reagent (plasmid)          | pRK5-Gqi9                                          | AddGene                                                                                            | 125711               |                                                                                                                  |
| recombinant DNA reagent (plasmid)          | pcDNA3.1(+)-G5A                                    | this study                                                                                         | N/A                  | sequence information provided in Supplementary file 7                                                            |
| recombinant DNA reagent (plasmid)          | pcDNA3.1(+)-Gqi5/9                                 | this study                                                                                         | N/A                  | sequence information provided in Supplementary file 7                                                            |
| recombinant DNA reagent                    | cloned N. vectensis GPCRs in pcDNA3.1(+)           | identified in this study                                                                           | N/A                  | full list of cloned GPCRs with sequences in Supplementary file 8                                                 |
| recombinant DNA reagent                    | synthesized N. vectensis GPCRs in pcDNA3.1(+)      | identified in this study, codon optimized and synthesized by GenScript                             | N/A                  | full list of synthesized GPCRs with original and codon optimized sequences in Supplementary file 8               |
| sequence-based reagent                     | cloning primers to create Gqi5/9                   | this study                                                                                         | N/A                  | sequence information provided in Supplementary file 7                                                            |
| sequence-based reagent                     | GPCR cloning primers                               | this study                                                                                         | N/A                  | full list of primers with sequences in Supplementary file 8                                                      |
| peptide, recombinant protein               | custom peptides                                    | identified in this study, synthesized by GenScript                                                 | N/A                  | full list of peptides with sequences and purity in Supplementary file 2 and 3                                    |
| commercial assay or kit (PCR clean up)     | Monarch® PCR & DNA Cleanup Kit (5 μg)              | New England Biolabs                                                                                | T1030L               |                                                                                                                  |
| commercial assay or kit (Miniprep)         | GeneJET Plasmid Miniprep Kit                       | Thermo Fisher Scientific                                                                           | K0503                |                                                                                                                  |
| strain, strain background (E. coli, TOP10) | One Shot™ TOP10 Chemically Competent E. coli       | Thermo Fisher Scientific                                                                           | C404010              | E. coli strain used for general cloning                                                                          |
| cell line (HEK293)                         | HEK293 Cells expressing GFP-AEQUORIN in Cytoplasma | Angio-Proteomie                                                                                    | cAP-0200GFP-AEQ-Cyto |                                                                                                                  |
| chemical compound, drug                    | DMEM                                               | Gibco (from ThermoFisher)                                                                          | 10566016             |                                                                                                                  |
| chemical compound, drug                    | OptiMEM                                            | Gibco (from ThermoFisher)                                                                          | 11058021             |                                                                                                                  |
| chemical compound, drug                    | FBS                                                | Gibco (from ThermoFisher)                                                                          | 10500064             |                                                                                                                  |
| chemical compound, drug                    | PEI (Polyethylenimine, 25k Mw)                     | Sigma-Aldrich                                                                                      | 408727               | used 0.3 µl of a 1 mg/ml stock solution per 100 ng DNA                                                           |
| chemical compound, drug                    | Transfectamine 5000                                | AAT Bioquest                                                                                       | 60022                | used 0.3 µl per 100 ng of DNA                                                                                    |
| chemical compound, drug                    | Coelenterazine-h                                   | Promega                                                                                            | S2011                | diluted to 2 mM in Ethanol and used at a final concentration of 4 µM in the assays                               |
| chemical compound, drug                    | TRIzol™ Reagent                                    | Invitrogen (from ThermoFisher)                                                                     | 15596026             |                                                                                                                  |
| other                                      | Corning® 96 Well White Polystyrene Microplate      | Corning (from Sigma-Aldrich)                                                                       | CLS3903              | cell culture treated assay plates                                                                                |
| other                                      | Nunc™ EasYFlask™ T75 Cell Culture Flasks           | Nunc (from ThermoFisher)                                                                           | 156499               | cell culture flasks                                                                                              |
| other                                      | Flexstation 3 Multimode Microplate Reader          | Molecular Devices                                                                                  |                      | plate reader                                                                                                     |
| software, algorithm                        | SoftMax®  Pro 7                                    | Molecular Devices                                                                                  |                      |                                                                                                                  |
| software, algorithm                        | R                                                  | https://cran.rstudio.com/                                                                          |                      |                                                                                                                  |
| software, algorithm                        | RStudio                                            | https://posit.co/download/rstudio-desktop/                                                         |                      |                                                                                                                  |
| software, algorithm                        | SignalP4.1                                         | https://services.healthtech.dtu.dk/services/SignalP-6.0/                                           |                      |                                                                                                                  |
| software, algorithm                        | NeuroPID                                           | https://bio.tools/neuropid                                                                         |                      |                                                                                                                  |
| software, algorithm                        | HMMER3.1b2                                         | http://hmmer.org/download.html                                                                     |                      |                                                                                                                  |
| software, algorithm                        | CD-HIT                                             | https://sites.google.com/view/cd-hit                                                               |                      |                                                                                                                  |
| software, algorithm                        | TransDecoder                                       | https://github.com/TransDecoder/TransDecoder                                                       |                      |                                                                                                                  |
| software, algorithm                        | CLANS (desktop version)                            | https://mybiosoftware.com/clans-20101007-visualize-protein-families-based-pairwise-similarity.html |                      |                                                                                                                  |
| software, algorithm                        | CLANS (online toolkit)                             | https://toolkit.tuebingen.mpg.de/tools/clans                                                       |                      |                                                                                                                  |
| software, algorithm                        | Phobius                                            | https://phobius.sbc.su.se/data.html                                                                |                      |                                                                                                                  |
| software, algorithm                        | muscle alignment tool                              | https://drive5.com/muscle5/                                                                        |                      |                                                                                                                  |
| software, algorithm                        | MAFFT v7                                           | https://mafft.cbrc.jp/alignment/software/                                                          |                      |                                                                                                                  |
| software, algorithm                        | trimAl                                             | http://trimal.cgenomics.org/trimal                                                                 |                      |                                                                                                                  |
| software, algorithm                        | IQ-tree2                                           | http://www.iqtree.org/                                                                             |                      |                                                                                                                  |
| software, algorithm                        | Fasttree                                           | http://www.microbesonline.org/fasttree/                                                            |                      |                                                                                                                  |

@@

@@

```{r}
#| echo: false
2 * 2
```

@@

>>>>

---
title: "R course report - group 1"
author: "name1, name2, name3"
format: html
---

## Quarto
### Heading 2
#### Heading 3

@@

@@

```{r}
print('hi, this is an R command executed')
```

```{bash}
echo hi
```

@@

```{r}
#| echo: false
#| eval: true
2 * 2
```

@@

## Next section

### 2024-11-11 presentation/RStudio_paper_writing_course_presentation.qmd
MS, presentation: edits, update git slide

## Part 6 - Collaborative code and paper writing with Rstudio and GitHub

@@

-   GitHub www.github.com is a platform for software development and version control
-   owned by Microsoft since 2018
-   developers can have public and private repositories
-   can share repositories privately with collaborators
-   integrates well with Rstudio
-   uses git protocol that is open source and also used by other code-hosting sites

>>>>

## Part 6 - Collaborative code and paper writing with Rstudio and git

@@

-   git is an open source program and protocol for version control
- several online platforms were built to make code sharing with git easier
- GitHub www.github.com is one such platform
- GitHub is owned by Microsoft since 2018
- developers can have public and private repositories
- can share repositories privately with collaborators
- integrates well with Rstudio
